HGP analysis: fit model

### 2019-03-26 rick/final/3_fit_model_compareModels.Rmd
update

#chr <- args[3]
chr <- 'PublishedVariants'

@@

```{r}
library(tidyverse)
library(lfa)
library(furrr)
library(glm2)
library(tictoc)
library(data.table)
library(cowplot)
options(future.globals.maxSize= 25000000000)
plan(multicore)
```
load plink format genotype data
```{r}
data_genotype <- read.bed(paste0(plinkPath,'chr',chr))

>>>>

#chr <- args[3]
plinkName <- 'PublishedVariants'

@@

```{r}
library(tidyverse)
library(lfa)
library(furrr)
library(glm2)
library(tictoc)
library(data.table)
library(cowplot)
options(future.globals.maxSize= 25000000000)
plan(multicore)
```
load plink format genotype data
```{r}
data_genotype <- read.bed(paste0(plinkPath,plinkName))
